### 2015-05-19 writing/SNLI paper/model_structure_fig.tex
Transfer update; new figure.

\begin{figure}[tp]
  \centering
    \footnotesize

	\newcommand{\labeledtreenode}[4][3]{\put(#2){\makebox(0,0){{\fcolorbox{black}{#4}{\makebox(#1,0.3){#3}}}}}}

	\newcommand{\textlabel}[4][3.5]{\put(#2){\makebox(0,0){{\makebox(#1,0.3){#3}}}}}

	\definecolor{lexcolor}{HTML}{F5F7C4}
	\definecolor{compositioncolor}{HTML}{BBEBFF}
	\definecolor{comparisoncolor}{HTML}{FFC895}
	\definecolor{softmaxcolor}{HTML}{A5FF8A}

	\setlength{\unitlength}{0.61cm}

	%\resizebox{3in}{!}{
	\begin{picture}(13.15, 5.5)

	  \labeledtreenode[5]{6.5,6.5}{softmax classifier}{softmaxcolor}  
	  \put(6.5,5.25){\vector(0,1){1}}  
	  \labeledtreenode[5]{6.5,5.25}{$\tanh$ layer}{comparisoncolor}
	  \put(6.5,4){\vector(0,1){1}}  
	  \labeledtreenode[5]{6.5,4}{$\tanh$ layer}{comparisoncolor}	 
	  \put(6.5,2.75){\vector(0,1){1}}  
           \labeledtreenode[5]{6.5,2.75}{$\tanh$ layer}{comparisoncolor}

	  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

	  \put(3,1.5){\vector(2,1){0.85}}
	  \labeledtreenode{1.5,1.5}{turtle}{lexcolor}

	  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

	\end{picture}
	%}
        \caption{The standard model structure used for entailment evaluation.}
  \label{sample-figure}
\end{figure}

>>>>

\begin{figure}[tp]
  \centering

 \begin{tikzpicture}
    \def\dx{19pt}
    \def\dy{29pt}

    \tikzstyle{label}=[text width=40mm,align=center]    
    \tikzstyle{softmax}=[fill=red!40,text width=40mm,align=center]
    \tikzstyle{preclass}=[fill=orange!40,text width=50mm,align=center]
    \tikzstyle{e}=[fill=green!40,text width=25mm,align=center]
    \tikzstyle{m}=[fill=blue!40,text width=34mm,align=center]

    \node[softmax]  (softmax) at (0*\dx,6*\dy) {3-way softmax classifier};
    \node[preclass]  (pc3) at (0*\dx,5*\dy) {100d $\tanh$ layer};
    \node[preclass]  (pc2) at (0*\dx,4*\dy) {100d $\tanh$ layer};
    \node[preclass]  (pc1) at (0*\dx,3*\dy) {100d $\tanh$ layer};
    \node[e]  (pe) at (-3*\dx,1.85*\dy) {50d premise};
    \node[e]  (he) at (3*\dx,1.85*\dy) {50d hypothesis};
    \node[m]  (pem) at (-3*\dx,0.5*\dy) {embedding model\\ with premise input};
    \node[m]  (hem) at (3*\dx,0.5*\dy) {embedding model\\ with hypothesis input};

    \pgfsetarrowsend{latex}
    \tikzstyle{fwd} = [draw=black, line width=1pt]

          \draw [fwd] (pc3) -- (softmax);
          \draw [fwd] (pc2) -- (pc3);
          \draw [fwd] (pc1) -- (pc2);
          \draw [fwd] (pe) -- (pc1);
          \draw [fwd] (he) -- (pc1);
          \draw [fwd] (hem) -- (he);
          \draw [fwd] (pem) -- (pe);

  \end{tikzpicture}

        \caption{The standard model structure used for entailment evaluation.}
  \label{sample-figure}
\end{figure}
